\documentclass{article}

\usepackage{tabularx}
\usepackage{booktabs}

\title{Problem Statement and Goals\\\progname}

\author{\authname}

\date{}

\input{../Comments}
\input{../Common}

\begin{document}

\maketitle

\begin{table}[hp]
\caption{Revision History} \label{TblRevisionHistory}
\begin{tabularx}{\textwidth}{llX}
\toprule
\textbf{Date} & \textbf{Developer(s)} & \textbf{Change}\\
\midrule
September 23, 2024 & NFI, JL, CG, AV & Initial Draft\\
... & ... & ...\\
\bottomrule
\end{tabularx}
\end{table}

\newpage{}

\section{Problem Statement}

\subsection{Background}

The McMaster GSA softball league is used every summer by 30-40 teams and
as many as 1,000 unique participants. The league is currently organized through
an old software platform accessible via a web browser, but it is outdated and
does not include features for administrators to maintain the site without
extensive knowledge of computer programming. The GSA league is aware that
paid-for and ad-supported services are available, and features present in
those applications should be explored and added if possible. The GSA league
is a minimal-cost non-profit and would like a personalized platform by which
to operate without committing to paid-for services. Some players find the
current website UI difficult to use and unstable, and would prefer a more
intuitive solution that needs little to no maintenance.

\subsection{Problem}

The platform will be responsible for including all functionalities
of the current solution such as scheduling, division management,
communication between captains, waiver management, rescheduling, score and
league standings management, and other tasks identified by the stakeholders.
Our solution would be an updated form of the existing website's capabilities
with a modernized UI and the additional features of player-specific logins,
real-time standings, and commisioner announcements. Additionally, enhanced
stability is key in replacing the lack of maintainability of the current
website. 

\subsection{Inputs and Outputs}

\subsubsection{Inputs}

\begin{itemize}
    \item Player/Captain/Commissioner login information
    \item Player/Captain/Commissioner contact information
    \item Team information
    \item Game score
    \item Captain/Team availability
    \item Reschedule requests
    \item Commissioner announcements
\end{itemize}

\subsubsection{Outputs}

\begin{itemize}
    \item League standings
    \item League scheduling
    \item Commissioner announcements
\end{itemize}

\subsection{Stakeholders}

\begin{itemize}
    \item The supervisor of the project, Dr. Jake Nease
    \item Commissioners of the league
    \item Captains/Players/Umpires of the softball league
    \item Administrators of the scheduling tool
    \item Spectators
\end{itemize}

\subsection{Environment}

\begin{description}
    \item [Software] Windows, Linux or Mac OS
    \item [Hardware] Computers with access to the internet
\end{description}

\section{Goals}

\begin{description}
    \item [Accomplish everything the existing league website does]
    The original league website functionality should be recreated in the
    solution. The current website allows captains to log in and record 
    their matches and scores. It allows scheduling and rescheduling, and
    provides a place to see the league rules, parking information and
    other information.
    \item [User interface should be intuitive to all users.] The current
    interface is unintuiative and awkward to use. Users should understand
    how to log in and how to view their schedule just by looking at their
    homepage. No external information should be required.
    \item [Allow players to make accounts] Currently, only captains have
    accounts in the system. Player accounts should only be able to view the
    contact information of their team captain, captains should only be able
    to view the contact of their players and other captains, and commisioners
    should be able to see everything.
    \item [Matches should be able to be scheduled and rescheduled.] 
    Team captains should be able to give their team's availablity and the
    software will algorithmically schedule the season's matches. If a team
    isn't available for a match after it has been scheduled, captains can
    send a reschedule request with a selection of possible alternative times
    that the opposition team's captain can agree to.
    \item [Solution should be maintainable and robust] 
    Currently, the website in use is maintained by one administrator, and
    requires constant maintainance. The website often breaks, requiring 
    the current administrator to fix issues as they arise. Some site 
    functions are prone to breaking or are broken. The new solution should 
    be robust enough to not require frequent intervention from an administrator.
    The solution should be maintainable; if issues do arise, the solution  
    should be well-documented such that non-domain experts are able to 
    solve the issues.
\end{description}

\section{Stretch Goals}

\begin{description}
    \item [Commisioners should be able to "rain out" matches] After a match
    has been scheduled, commisioner level accounts should be able to force
    a reschedule if the weather makes the game unreasonable to play. This
    will send a notification to the two team captains so they can
    choose a date that works.
    \item [League template saving] A season's teams and players should be
    able to be saved as a template that can be loaded the next season. This
    is useful as many teams remain the same or similar between seasons, and
    it would be convienient for all returning teams to avoid reinviting all
    returning players.
    \item [A mobile application companion] Users would be able to perform
    some actions they can on the website, like viewing schedules and
    standings from their mobile device.
\end{description}

\section{Challenge Level and Extras}

\subsection{Challenge Level}
\begin{description}
    \item[Challenge level:] General
    \item[Rationale:] Does not involve any extensive research and it is an
    improvement of an already existing solution.
\end{description}

\subsection{Extras}
\begin{itemize}
    \item Code walkthroughs
    \item User documentation
\end{itemize}

\newpage{}

\section*{Appendix --- Reflection}

\subsection*{Reflection -- Nicholas Fabugais-Inaba}

Majority of the deliverable went well resulting from the information
the team had received in our initial meeting with the supervisor of the
project, Dr. Jake Nease. He was able to detail many of the expectations
he had relating to the information required for the deliverable such as
the inputs, outputs, stakeholders, and goals. Only minimal brainstorming
was required from the team to fill in the rest of the information for the
deliverable. \newline

Certain pain points the team did experience, while writing this deliverable,
related to the problem the project would be addressing. Although some of
the information was gathered from the project description, which was listed
in the potential project document, provided to students, the team
still needed to address other crucial information that may not have
initially come to mind. This was resolved from the collective effort of
the team, brainstorming further resolutions as to why this problem needs
our specific solution. \newline

The team was able to adjust the scope of the goals, based on complexity,
by separating the primary goals of the project with the stretch goals.
Goals such as replicating the current features the exisiting website
possesses, having an easy-to-use interface, and a login system, make sure
the Capstone project isn't too overly ambitious and definitely achievable.
The stretch goals help to add complexity to create a senior design project
as developing a mobile version of the system and other additional features
are extra add-ons that add to the bulk of the work needed to be completed.

\subsection*{Reflection -- Alex Verity}

Writing the goals went smoothly, as we were able to use the notes taken during
the initial supervisor meeting directly when making the goals. We also easily
decided on extras for section four, as the supervisor requested for the code
to be explained thorougly.\newline

A particular pain point was finalizing the problem statement, as I find
writing problem statements to be difficult. They require a lot of information
given in a very short statement, which can be difficult. They also require
the author to not describe a possible solution, but to only lay out the
problem and I often feel compelled to add unnessecary details such as the
language we plan to use. It is also difficult to make sure we are not missing
out on any important elements of our problem.\newline

We accounted for scope by making sure we are happy with our stretch goals if
we require them to increase the complexity of our project. I believe they are
useful additions that would make the project more interesting and present
additional layers if we choose to persue them. We also made sure we have plans
for staying productive to make sure we can complete our goals, although we may
course correct down the line if necessary.

\subsection*{Reflection -- Casra Ghazanfari}

Writing the “Challenge Level and Extras” section of this deliverable went
very well for our team. From the beginning, we had no doubts about the challenge
level of our project because the professor’s description of the different levels
had made it clear to us as a team which level our project fell into.
Additionally, there was no disagreement on which extras we wanted to tackle for
this project. We had a very short discussion discussing the extras we were
interested in, which happened to almost perfectly match, making the decision
very quick and easy. \newline

A particular pain point our team faced during this deliverable was the inputs
and outputs section. Initially, we found it difficult to think of our systems
inputs and outputs without a particular implementation in our mind. We resolved
this by shifting our thinking from implementation to high-level design. Through
this mindset shift we were able to come up with more vague, high-level, and
implementation agnostic inputs and outputs for our system that conveyed ideas
rather than implementations. \newline

Our team adjusted the scope of our goals using two key rules. First, we made
sure that all of our goals were features/capabilities that the stakeholders
of the project would consider necessary for the project to be considered
“complete” or “fully-functional”. This ensured that our goals didn’t stray too
far from the base idea of the project, meaning that they couldn’t stray into
either overly ambitious or low complexity territory. Second, we made a clear
distinction in our minds between goals and stretch goals to ensure that we
didn’t blur the lines between them. Any goal that we deemed to be a
“nice to have” feature or “not completely necessary” we classified as a stretch
goal. We could not realistically guarantee any of these stretch goals would be
met due to their lack of necessity and therefore made sure they were not
considered goals, allowing us to keep our more ambitious ideas in check.

\subsection*{Reflection -- Jung Woo Lee}

For this deliverable, having the interview with the supervisor gave us all the
necessary information to fill out this document with ease. The background, 
problem, inputs and outputs, goals and stretch goals were all discussed to 
some extent, giving us a lot of information to work with and confidence that 
what we have written is desired and makes sense. \newline

One pain point was an apparent lack of outputs. This troubled me as I saw many
inputs and thought there should be more outputs than we had. Discussion with the
team relieved my worries as the current outputs are broad and encompassing, as 
well as the fact that this first revision will not get everything correct and we
will have the chance to revise this later. Another pain point were the goals, as 
I felt some were overlapping and could cause issues later. Discussion with my 
teammate led to the conclusion that although there are overlaps, the goals were 
important enough to expand upon on their own, even if another goal technically 
encompassed it. Lastly, I felt as though there were not enough goals relating to 
non-functional aspects of the solution, and thinking ahead, I believed it would 
be in our interest to include one. After discussion with the team, it was decided 
to replace one weaker goal with another non-functional goal of robustness and 
maintainability. \newline

With the initial interview with the supervisor, the team was able to clearly 
differentiate between possible goals the solution would likely require, and goals
that can be achieved once the main solution is completed. We avoided lofty goals 
and kept them grounded, ensuring the goals corresponded to the necessities of the 
solution. We ensured that the goals would allow us to challenge ourselves and 
force us to take on a learning curve that we deemed appropriate. For added 
complexity, stretch goals were made as discussed with the supervisor. These will 
be taken on if it is deemed that the solution is completed and the extra features
are feasible.

\end{document}